---
title: "Cabbages"
author: "Marta Marriott!"
date: "2/7/2024"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
### Plot boxplots

```{r}
boxplot(VitC~Cult,data=veggy)
```
  
The boxplot shows VitC over Cult, and the data within is reflects  the data collected.c52 in higher when comparison to c39. The median for c52 is roughly 65, where the median for c39 is about 52.   
  
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```
The comparison between the two data analysis from boxplot c39 and c52, gives the precise median for both and gives additional data such as height,which is represented in Q1 and Q3 respectively.They show statistical differences when the data point are compared.
  
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
t.test(VitC~Cult,data=veggy)
```
The data point collected is 0.00000003405 showing it is quite small and the difference reflects that between the two groups where the data is collected c39 and c52 there is a 95% difference when comparing the two groups, as they are both statistically different.
  
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps aref related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

We used the necessary tools and methods in order to show the statistical differences from the data plot point in veggy. We first created a boxplot to visually represent what is happening with the data.Secondly, we used numerical description to show numerically the statistical differences by comparing the data shown in the boxplot. Lastly, a t-test was run to show how statistically different the two points actually were to understand they had a 95% difference from each other and  therefore explains  the different data points in the boxplot and numerical data.

